---
title: "Checks Report"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document: default
params:
  data:
    label: "Dataset to analyze"
    value: data
  threshold:
    value: 90
  un_estimates:
      value: un_estimates
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE)
```

```{r}
library(cd2030)
library(dplyr)
library(gt)
```

### Health facility data quality assessment: numerators

**BACKGROUND:** Routinely reported health facility data are an important data source for health indicators. The data are reported by health facilities on events such as immunizations given, or live births attended. As with any data, quality is an issue. Data are checked to consider completeness of reporting by health facilities, identify extreme outliers and internal consistency. 


```{r}
rows <- c("1a", "1b", "1c", "2a", "2b", "3f", "3g", "3h", "3i", "3j", '4')

calculate_overall_score(params$data) %>% 
  gt() %>%
          tab_header(
            title = md("**Table 1a: Summary of data quality for reported immunization health facility data**")
          ) %>%
          tab_row_group(
            label = "3. Consistency of annual reporting",
            rows = no %in% c("3a", "3b", '3c', '3d', '3e', '3f', '3g', '3h', '3i', '3j')
          ) %>%
          tab_row_group(
            label = "2. Extreme outliers (Common Vaccine antigens)",
            rows = no %in% c("2a", "2b")
          ) %>%
          tab_row_group(
            label = "1. Completeness of monthly facility reporting (Immunization)",
            rows = no %in% c("1a", "1b", "1c")
          ) %>%
          tab_style(
            style = cell_fill(color = "lightgoldenrodyellow"),
            locations = cells_row_groups()
          ) %>%
          fmt_number(
            columns = starts_with("20"),
            rows = no %in% rows,
            decimals = 1
          ) %>%
          fmt_number(
            columns = starts_with("20"),
            rows = !no %in% rows,
            decimals = 2
          )
```

```{r}
plot(calculate_district_reporting_rate(params$data, params$threshold)) +
  cd_report_theme()
```


### Health facility data quality assessment: numerators

**BACKGROUND:** Routinely reported health facility data are essential for monitoring 
immunization coverage. Data quality assessments often reveal discrepancies in the 
Penta1/Penta3 ratio, which should ideally be close to 1.


```{r}
plot(calculate_ratios_summary(params$data, ratio_pairs = list(ratioAP = c("anc1", "penta1"), ratioPP = c("penta1", "penta3"),
    ratioOO = c("opv1", "opv3")))) +
  cd_report_theme()
```

### Health facility data adjustment: Numerators - reported live births and Pentavalent 1 doses

**BACKGROUND:** Completeness of reporting affects analysis, especially if it is 
low or varies between years. Extreme outliers can have a large impact, especially
on subnational numbers. Several steps are necessary to obtain a clean data set for
“endline” analysis, including adjusting for incomplete reporting and correcting
for extreme outliers. These graphs show the impact on the numbers.

```{r}
plot(prepare_population_metrics(params$data, un_estimates = params$un_estimates), metric = 'population') +
  cd_report_theme()
```

```{r}
plot(prepare_population_metrics(params$data, un_estimates = params$un_estimates), metric = 'births') +
  cd_report_theme()
```

