---
title: "Checks Report"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document: default
params:
  data:
    label: "Dataset to analyze"
    value: data
  threshold:
    value: 90
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE)
```

```{r}
library(cd2030)
library(gt)
```

### Reporting Rate

#### Average RR by year

```{r}
params$data %>% 
  check_average_reporting_rate() %>% 
  gt() %>% 
  tab_header(title = 'Table 1 - average reporting rates for all indicators, by year')
```

#### Reporting Rate District {.tabset}

##### RR >= `r params$threshold` (districts)

```{r}
dt <- params$data %>% 
  check_district_reporting_summary(threshold = params$threshold) 

dt %>% 
  gt() %>% 
  tab_header(title = paste0('Table 2 - Percentage of districts with reporting rates >=', params$threshold, ' by year'))
```

##### Low RR districts (graph)

```{r}
plot(dt)
```

##### {-}

### Internal Consitency {.tabset}

#### IPV1 vs IPV2 ratio

```{r}
plot_comparison_ipv1_ipv2(params$data)
```

#### OPV1 vs OPV3 ratio

```{r}
plot_comparison_opv1_opv3(params$data)
```

#### OPV1 vs ANC1 ratio

```{r}
plot_comparison_opv1_anc1(params$data)
```

#### OPV1 vs Penta1 ratio

```{r}
plot_comparison_opv1_penta1(params$data)
```

#### OPV3 vs Penta3 ratio

```{r}
plot_comparison_opv3_penta3(params$data)
```

#### PCV1 vs PCV3 ratio

```{r}
plot_comparison_pcv1_pcv3(params$data)
```

#### PCV3 vs Penta3 ratio

```{r}
plot_comparison_pcv3_penta3(params$data)
```

#### Penta1 vs ANC1 ratio

```{r}
plot_comparison_penta1_anc1(params$data)
```

#### Penta1 vs PCV1 ratio

```{r}
plot_comparison_penta1_pcv1(params$data)
```

#### Penta1 vs Penta2 ratio

```{r}
plot_comparison_penta1_penta2(params$data)
```

#### Rota1 vs Rota2 ratio

```{r}
plot_comparison_rota1_rota2(params$data)
```

#### {-}

### Adequate ratios

```{r}
params$data %>% 
  check_ratios() %>% 
  gt() %>% 
  tab_header(title = 'Table 3 - Percentage of districts with adequate ratios (between 1.0 and 1.5)')
```

### Outliers

#### Outliers by year

```{r}
params$data %>% 
  check_outlier_summary() %>% 
  gt() %>% 
  tab_header(title = 'Table 4 - Percentage of monthly values that are not extreme outliers, by year')
```

#### Outliers (Districts)

```{r}
params$data %>% 
  check_outlier_district() %>% 
  gt() %>% 
  tab_header(title = 'Table 5 - Percentage of districts with no extreme outliers, by year')
```

### Missings

#### Missing by years

```{r}
params$data %>% 
  check_missing_summary() %>% 
  gt() %>% 
  tab_header(title = 'Table 6 - Percentage of monthly values that are not missing, by year')
```

#### Missings (districts)

```{r}
params$data %>% 
  check_missing_district() %>% 
  gt() %>% 
  tab_header(title = 'Table 7 - Percentage of districts with no missing values, by year')
```
