---
title: "Countdown Analysis Report for `r params$country`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document: default
  pdf_document:
    toc: true
params:
  data:
    label: "Dataset to analyze"
    value: data
  threshold:
    value: 90
  survey_values:
    value: survey_values
  k_factors:
    value: !r c(anc = 0.25, idelv = 0.25, vacc = 0.25)
  denominator:
    value: dhis2
  survey_start_year:
    value: 2015
  country:
    value: Country
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)
```

```{r}
library(cd2030)
library(dplyr)
library(gt)
library(reactable)
library(gridExtra)

rates <- survey_values$rates
national_data <- survey_values$data
un_estimates <- national_data$un
wuenic_estimates <- national_data$wuenic
survdata <- national_data$survdata %>% 
  filter(year >= params$survey_start_year)
gregion <- national_data$gregion %>% 
  filter(year >= params$survey_start_year)
subnational_map <- national_data$map_map
```

## 1. Health Facility Data Quality Assessment

### Background

Routinely reported health facility data are an important data source for health
indicators. The data are reported by health facilities on events such as immunizations
given, or live births attended. As with any data, quality is an issue. Data are checked
to consider completeness of reporting by health facilities, identify extreme outliers
and internal consistency. 

::: {.box}
#### Interpretation Guidance
- Identify trends in completeness of reporting.
- Note any districts with extreme outliers and inconsistencies.
:::

### Results

#### Data Quality Sumary Table

```{r, results='asis'}
rows <- c("1a", "1b", "1c", "2a", "2b", "3f", "3g", "3h", "3i", "3j", '4')

# calculate_overall_score(params$data) %>%
#   gt() %>%
#           tab_header(
#             title = md("**Table 1a: Summary of data quality for reported immunization health facility data**")
#           ) %>%
#           tab_row_group(
#             label = "3. Consistency of annual reporting",
#             rows = no %in% c("3a", "3b", '3c', '3d', '3e', '3f', '3g', '3h', '3i', '3j')
#           ) %>%
#           tab_row_group(
#             label = "2. Extreme outliers (Common Vaccine antigens)",
#             rows = no %in% c("2a", "2b")
#           ) %>%
#           tab_row_group(
#             label = "1. Completeness of monthly facility reporting (Immunization)",
#             rows = no %in% c("1a", "1b", "1c")
#           ) %>%
#           tab_style(
#             style = cell_fill(color = "lightgoldenrodyellow"),
#             locations = cells_row_groups()
#           ) %>%
#           fmt_number(
#             columns = starts_with("20"),
#             rows = no %in% rows,
#             decimals = 1
#           ) %>%
#           fmt_number(
#             columns = starts_with("20"),
#             rows = !no %in% rows,
#             decimals = 2
#           )

# data <- calculate_overall_score(params$data) %>%
#   mutate(
#     Group = case_when(
#       no %in% c("3a", "3b", "3c", "3d", "3e", "3f", "3g", "3h", "3i", "3j") ~ "3. Consistency of annual reporting",
#       no %in% c("2a", "2b") ~ "2. Extreme outliers (Common Vaccine antigens)",
#       no %in% c("1a", "1b", "1c") ~ "1. Completeness of monthly facility reporting (Immunization)",
#       TRUE ~ "Other"
#     )
#   )
# 
# reactable(
#   data,
#   groupBy = "Group",
#   columns = list(
#     no = colDef(name = "Indicator"),
#     defaultColDef = colDef(
#       align = "center",
#       format = colFormat(digits = 1)
#     )
#   ),
#   highlight = TRUE
# )

```

#### District Reporting Rates

```{r district-reporting-rates}
plot(calculate_district_reporting_rate(params$data, params$threshold)) +
  cd_report_theme()
```

---

## 2. Health Facility Data Adjustments

### Background

Routinely reported health facility data are essential for monitoring immunization
coverage. Data quality assessments often reveal discrepancies in the  Penta1/Penta3 ratio, which should ideally be close to 1.


```{r}
plot(calculate_ratios_summary(params$data, ratio_pairs = list(ratioAP = c("anc1", "penta1"), ratioPP = c("penta1", "penta3")))) +
  cd_report_theme()
```

### Health facility data adjustment: Numerators - reported live births and Pentavalent 1 doses

**BACKGROUND:** Completeness of reporting affects analysis, especially if it
is low or varies between years. Extreme outliers can have a large impact,
especially on subnational numbers. Several steps are necessary to obtain a
clean data set for “endline” analysis, including adjusting for incomplete
reporting and correcting for extreme outliers. These graphs show the impact
on the numbers.

```{r}
adjustments <- params$data %>%
  generate_adjustment_values(adjustment = 'custom', k_factors = params$k_factors)
```

```{r}
plot(adjustments,
     indicator = 'ideliv',
     title = 'Figure 1c: Comparison of number of live births before and after adjustments for completness and outliers') +
  cd_report_theme()
```

```{r}
plot(adjustments,
     indicator = 'penta1',
     title = 'Figure 1d: Comparison of number of penta1 vaccination before and after adjustments for completness and outliers') +
  cd_report_theme()
```

```{r}
plot(adjustments,
     indicator = 'bcg',
     title = 'Figure 1e: Comparison of number of BCG vaccination before and after adjustments for completness and outliers') +
  cd_report_theme()
```

```{r}
plot(adjustments,
     indicator = 'measles1',
     title = 'Figure 1f: Comparison of number of measles vaccination before and after adjustments for completness and outliers') +
  cd_report_theme()
```


### Health facility data denominator assessment: DHIS2,  UN Population and livebirths projections

**BACKGROUND:** Service coverage is defined as the population who received the
service divided by the population who need the services: the denominator. The
quality of the population projections in DHIS2 is assessed through
consistency over time and comparison with the UN projections.


```{r}
plot(prepare_population_metrics(params$data, un_estimates = un_estimates), metric = 'population') +
  cd_report_theme()
```

```{r}
plot(prepare_population_metrics(params$data, un_estimates = un_estimates), metric = 'births') +
  cd_report_theme()
```

#### Selection of the best denominator 

```{r}
indicator_coverage <- params$data %>%
  calculate_indicator_coverage(un_estimates = un_estimates,
                               sbr = rates$sbr,
                               nmr = rates$nmr,
                               pnmr = rates$pnmr,
                               twin = rates$twin_rate,
                               preg_loss = rates$preg_loss,
                               anc1survey = rates$anc1,
                               dpt1survey = rates$penta1)

plot_absolute_differences(indicator_coverage, 'penta3') +
  cd_report_theme()
plot_absolute_differences(indicator_coverage, 'measles1') +
  cd_report_theme()
plot_absolute_differences(indicator_coverage, 'bcg') +
  cd_report_theme()
```

## National Estimates

### National Vaccination Coverage trends using all sources of data

**BACKGROUND:** Monitoring the coverage of interventions is a critical and
direct output of health systems. It is most useful if the national plan has
meaningful targets. Both health facility and survey data need to be used.


```{r}
measles1_coverage <- analyze_coverage(params$data,
                         indicator = 'measles1',
                         denominator = params$denominator,
                         un_estimates = un_estimates,
                         wuenic_data = wuenic_estimates,
                         survey_data = survdata,
                         sbr = rates$sbr,
                         nmr = rates$nmr,
                         pnmr = rates$pnmr,
                         anc1survey =rates$anc1,
                         dpt1survey = rates$penta1,
                         twin = rates$twin_rate,
                         preg_loss = rates$preg_loss)

render_with_error_handling({
  plot(measles1_coverage) + cd_report_theme()
})

```

```{r}
penta3_coverage <- analyze_coverage(params$data,
                         indicator = 'penta3',
                         denominator = params$denominator,
                         un_estimates = un_estimates,
                         wuenic_data = wuenic_estimates,
                         survey_data = survdata,
                         sbr = rates$sbr,
                         nmr = rates$nmr,
                         pnmr = rates$pnmr,
                         anc1survey =rates$anc1,
                         dpt1survey = rates$penta1,
                         twin = rates$twin_rate,
                         preg_loss = rates$preg_loss)

render_with_error_handling({
  plot(penta3_coverage) + cd_report_theme()
})
```

## Regional Estimates

### Vaccination Access level (Pentavalent 1 – Pentavalent 3 dropout rates)

BACKGROUND: Monitoring the coverage of interventions is a critical and direct
output of health systems. It is most useful if the national plan has
meaningful targets. Both health facility and survey data need to be used.

```{r}

measles_subnational_coverage <- analyze_coverage(params$data,
                         admin_level = 'admin_level_1',
                         region = 'input$region',
                         subnational_map = subnational_map,
                         indicator = 'measles1',
                         denominator = params$denominator,
                         un_estimates = un_estimates,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates,
                         sbr = rates$sbr,
                         nmr = rates$nmr,
                         pnmr = rates$pnmr,
                         anc1survey =rates$anc1,
                         dpt1survey = rates$penta1,
                         twin = rates$twin_rate,
                         preg_loss = rates$preg_loss)
```

## Equity Analysis

### Regional Vaccination Coverage inequality using routine health facility data

**BACKGROUND:** Monitoring intervention coverage is a crucial output of health
systems, especially when national plans set clear and actionable targets. To
effectively assess vaccination coverage inequality at the subnational level,
particularly for MCV1 and Penta 3, it is essential to utilize both health
facility data and survey data. 

```{r}
penta3_inequality <- analyze_inequality(params$data,
                           level = 'admin_level_1',
                           indicator = 'penta3',
                           denominator =  params$denominator,
                           un_estimates = un_estimates,
                           sbr = rates$sbr,
                           nmr = rates$nmr,
                           pnmr = rates$pnmr,
                           anc1survey = rates$anc1,
                           dpt1survey = rates$penta1,
                           twin = rates$twin_rate,
                           preg_loss = rates$preg_loss)

render_with_error_handling({
  plot(penta3_inequality) + cd_report_theme()
})
```

```{r}
max_year <- max(params$data$year, na.rm = TRUE)
mapping_data <- get_mapping_data(params$data, un_estimates, rates, subnational_map)

render_with_error_handling({
  plot(mapping_data, indicator = 'penta3',
               denominator = params$denominator,
               palette = 'Greens',
               plot_year = max_year,
               title = paste("Distribution of Penta3 Coverage in ", params$country, "by Regions")) +
            cd_report_theme()
})
```

```{r}
measles1_inequality <- analyze_inequality(params$data,
                           level = 'admin_level_1',
                           indicator = 'measles1',
                           denominator =  params$denominator,
                           un_estimates = un_estimates,
                           sbr = rates$sbr,
                           nmr = rates$nmr,
                           pnmr = rates$pnmr,
                           anc1survey = rates$anc1,
                           dpt1survey = rates$penta1,
                           twin = rates$twin_rate,
                           preg_loss = rates$preg_loss)

render_with_error_handling({
  plot(measles1_inequality) + cd_report_theme()
})
```

```{r}
max_year <- max(params$data$year, na.rm = TRUE)
mapping_data <- get_mapping_data(params$data, un_estimates, rates, subnational_map)

render_with_error_handling({
  plot(mapping_data, indicator = 'measles1',
               denominator = params$denominator,
               palette = 'Blues',
               plot_year = max_year,
               title = paste("Distribution of Measles 1 Coverage in ", params$country, "by Regions")) +
            cd_report_theme()
})
```

### Equity Analysis

**BACKGROUND:** Household surveys provide critical information on inequalities. The focus is on two major dimensions of inequality: household
wealth quintile and education of the mother. Equiplots are used to assess
whether the country has made progress since 2010 in reducing the poor rich gap
or the gap between women with no education or low education and women with
higher education.

#### Equity analysis using survey data: Pentavalent 3 coverage by household wealth status and education

**Fig 4g: Pentavalent 3 coverage by wealth, recent surveys**
```{r}
equiplot_wealth(national_data$wiq, 'penta3') +
  cd_report_theme()
```

**Fig 4h: Pentavalent 3 coverage by level of education of the mother, recent surveys** 
```{r}
equiplot_education(national_data$meduc, 'penta3') +
  cd_report_theme()
```

**Fig 4g: Pentavalent 3 coverage by place of residence, recent surveys**
```{r}
equiplot_area(national_data$area, 'penta3') +
  cd_report_theme()
```

#### Equity analysis using survey data: Measles 1 coverage by household wealth status and education

**Fig 4g: Measles 1 coverage by wealth, recent surveys**
```{r}
equiplot_wealth(national_data$wiq, 'penta3') +
  cd_report_theme()
```

**Fig 4h: Measles 1coverage by level of education of the mother, recent surveys** 
```{r}
equiplot_education(national_data$meduc, 'penta3') +
  cd_report_theme()
```

**Fig 4g: Measles 1 coverage by place of residence, recent surveys**
```{r}
equiplot_area(national_data$area, 'penta3') +
  cd_report_theme()
```
