---
title: "Denominator Assessment for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document:
    toc: false
    reference_docx: report-template.docx
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)

library(cd2030)
library(dplyr)
library(purrr)
library(gt)
library(reactable)
library(gridExtra)

cache <- params$cache

adjusted_data <- cache$get_adjusted_data()
un_estimates <- cache$get_un_estimates()

# Function to print notes for a given page
print_notes <- function(page_id, object_id = NULL, parameters = NULL) {
  # Retrieve the notes from the cache
  page_notes <- cache$get_notes(page_id, object_id, parameters) %>% 
    filter(include_in_report == TRUE, !is.null(note))
  
  # Check if there are any notes
  if (nrow(page_notes) > 0) {
    page_notes %>% 
      pull(note) %>% 
      walk(~ cat(paste0(,x, '\n\n')))
  } else {
    cat(paste0("**--- Enter notes related to ", page_id, ' ', object_id, '. ---**\n\n'))
  }
}
```

## 3. Health facility data denominator assessment: DHIS2, UN Population and livebirths projections {-}

### Background

Service coverage is defined as the population who received the service divided by 
the population who need the services: the denominator. The quality of the population 
projections in DHIS2 is assessed through consistency over time and comparison with 
the UN projections.


### Total Population Projections: DHIS2 and UN Populations

```{r}
plot(prepare_population_metrics(adjusted_data, un_estimates = un_estimates), metric = 'population') +
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('denominator_assessment', 'Total Population')
```

---

:::

### Live Births Projections: DHIS2 and UN Live births

```{r}
plot(prepare_population_metrics(adjusted_data, un_estimates = un_estimates), metric = 'births') +
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('denominator_assessment', 'Births')
```

---

:::
