---
title: "Denominator Selection for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document:
    toc: false
    reference_docx: report-template.docx
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)

library(cd2030)
library(dplyr)
library(purrr)
library(gt)
library(reactable)
library(gridExtra)

cache <- params$cache

adjusted_data <- cache$get_adjusted_data()
un_estimates <- cache$get_un_estimates()
rates <- cache$get_national_estimates()

# Function to print notes for a given page
print_notes <- function(page_id, object_id = NULL, parameters = NULL) {
  # Retrieve the notes from the cache
  page_notes <- cache$get_notes(page_id, object_id, parameters) %>% 
    filter(include_in_report == TRUE, !is.null(note))
  
  # Check if there are any notes
  if (nrow(page_notes) > 0) {
    page_notes %>% 
      pull(note) %>% 
      walk(~ cat(paste0(,x, '\n\n')))
  } else {
    cat(paste0("**--- Enter notes related to ", page_id, ' ', object_id, '. ---**\n\n'))
  }
}
```

## 4. Selection of the best denominator {-}

### Background

Monitoring the coverage of interventions is a critical and direct output of health 
systems. It is most useful if the national plan has meaningful targets. Both health 
facility and survey data need to be used.

### Denominators selection based on Penta3 Coverage

```{r}
indicator_coverage <- adjusted_data %>%
  calculate_indicator_coverage(un_estimates = un_estimates,
                               sbr = rates$sbr,
                               nmr = rates$nmr,
                               pnmr = rates$pnmr,
                               twin = rates$twin_rate,
                               preg_loss = rates$preg_loss,
                               anc1survey = rates$anc1,
                               dpt1survey = rates$penta1)

plot_absolute_differences(indicator_coverage, 'penta3') +
  cd_report_theme()

```

#### 📝 Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('denominator_selection', 'Penta 3')
```

---

:::


### Denominator selection based on Measles 1 Coverage

```{r}
plot_absolute_differences(indicator_coverage, 'measles1') +
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('denominator_selection', 'Measles 1')
```

---

:::

### Denominator selection based on BCG Coverage


```{r}
plot_absolute_differences(indicator_coverage, 'bcg') +
  cd_report_theme()
```

#### 📝 Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('denominator_selection', 'BCG')
```

---

:::
