---
title: " `r params$country` - Countdown Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  officedown::rdocx_document:
    reference_docx: one-pager-template.docx
    page_size:
      width: 8.3
      height: 11.7
      orient: "portrait"
    page_margins:
      bottom: 0.5
      top: 1
      right: 0.5
      left: 0.5
      gutter: 0
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  dpi=300
)

library(cd2030)
library(dplyr)
library(purrr)
library(reactable)
library(gridExtra)
library(officedown)
library(officer)

cache <- params$cache

data <- cache$countdown_data
adjusted_data <- cache$adjusted_data
country <- cache$country
threshold <- cache$performance_threshold
k_factors <- cache$k_factors
rates <- cache$national_estimates
denominator <- cache$denominator
mapping_years <- cache$mapping_years
un_estimates <- cache$un_estimates
wuenic_estimates <- cache$wuenic_estimates
survey_start_year <- cache$start_survey_year
survdata <- cache$national_survey %>% 
  filter(if(is.null(survey_start_year)) TRUE else year >= survey_start_year)
gregion <- cache$regional_survey %>% 
  filter(if(is.null(survey_start_year)) TRUE else year >= survey_start_year)
subnational_map <- cache$survey_mapping
map_mapping <- cache$map_mapping
meduc <- cache$education_survey
wiq <- cache$wiq_survey
area <- cache$area_survey
selected_admin_level_1 <- cache$selected_admin_level_1
selected_district <- cache$selected_district
```

<!---BLOCK_MULTICOL_START--->

## Health Facility Data Quality

### Summary reported immunization health facility data DHIS2

```{r}

years <- unique(data$year)

data %>%
          calculate_overall_score(threshold) %>%
          mutate(
            type = case_when(
              no %in% c("1a", "1b", "1c") ~ '1. Completeness of monthly facility reporting (Immunization)',
              no %in% c("2a", "2b") ~ '2. Extreme outliers (Common Vaccine antigens)',
              no %in% c("3a", "3b",'3f', '3g') ~ '3. Consistency of annual reporting'
            )
          ) %>%
          as_grouped_data(groups = 'type') %>%
          as_flextable() %>%
          bold(j = 1, i = ~ !is.na(type), bold = TRUE, part = "body") %>%
          bold(part = "header", bold = TRUE) %>%
          colformat_double(i = ~ is.na(type) & !no %in% c("3a", "3b"), j = as.character(years), digits = 0, big.mark = ",") %>%
          colformat_double(i = ~ is.na(type) & no %in% c("3a", "3b"), j = as.character(years), digits = 2) %>%
          bg(
            i = ~ is.na(type) & !no %in% c("3a", "3b"),
            j = as.character(years),
            bg = function(x) {
              # Use map to apply function to each cell
              result <- map_chr(as.list(x), ~ {
                if (is.na(.x) || is.null(.x)) {
                  return("transparent")
                } else if (.x >= threshold) {
                  return("seagreen")
                } else if (.x >= 70 && .x < threshold) {
                  return("yellow")
                } else if (.x < 70) {
                  return("red")
                } else {
                  return("transparent")
                }
              })
              return(result)
            },
            part = "body"
          ) %>%
          bg(
            i = ~ !is.na(type), part = "body",
            bg = 'lightgoldenrodyellow'
          ) %>%
   fontsize(size = 7) %>% 
          theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```

`r officer::run_columnbreak()`

## Equity Analysis

### Wealth an urban-rural inequity for Penta 3 Coverage

#### Wealth

```{r, fig.width=3, fig.height=2.5}
equiplot_wealth(wiq, 'penta3') +
  cd_report_theme(base_size = 7)
```

#### Residence

```{r, fig.width=3, fig.height=2.5}
equiplot_area(area, 'penta3') +
  cd_report_theme(base_size = 7)
```

<!---BLOCK_MULTICOL_STOP{widths: [4,4], space: 0.2, sep: true}--->

DQA scores greater or equal to 90% are highlighted in green indicating good data quality, scores of 80-90% in yellow and less than 70% in red indicator poor data quality

<!---BLOCK_MULTICOL_START--->

## National immunization Coverage trends

### 2019 – 2023 trend in immunization coverage, first dose of measles, third dose of pentavalent vaccine's and pentavalent dropout rates

#### Measles 1

```{r, fig.width=3, fig.height=2.5}
national_coverage <- adjusted_data %>% 
  calculate_coverage(
    survey_data = survdata,
    wuenic_data = wuenic_estimates,
    un_estimates = un_estimates,
    sbr = rates$sbr,
    nmr = rates$nmr,
    pnmr = rates$pnmr,
    twin = rates$twin_rate,
    preg_loss = rates$preg_loss,
    anc1survey = rates$anc1,
    dpt1survey = rates$penta1
  )

plot(national_coverage, indicator = 'measles1', denominator = denominator) +
  cd_report_theme(base_size = 7)
```

#### Penta 3

```{r, fig.width=3, fig.height=2.5}
plot(national_coverage, indicator = 'penta3', denominator = denominator) +
  cd_report_theme(base_size = 7)
```

#### Penta1 to Penta3 Dropout

```{r, fig.width=3, fig.height=2.5}
plot(national_coverage, indicator = 'dropout_penta13', denominator = denominator) +
  cd_report_theme(base_size = 7)
```

`r officer::run_columnbreak()`

## Admin Level 1 Vaccination Coverage Map

### Subnational vaccination coverage 2019 & 2023 (measles1, penta3, dropout penta1_3)

#### Measles 1

```{r, fig.width=3, fig.height=2.5}
mapping_data <- get_mapping_data(adjusted_data, un_estimates, rates, map_mapping)

plot(mapping_data, 
     indicator = 'measles1',
     denominator = denominator,
     palette = 'Blues',
     plot_year = mapping_years) +
  cd_report_theme(base_size = 7) +
  theme(
    legend.text = element_text(size = 6),  
    legend.title = element_text(size = 7), 
    panel.border = element_blank(),     
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank(),
    panel.grid = element_blank(),
    aspect.ratio = 1
  )
```

#### Penta 3

```{r, fig.width=3, fig.height=2.5}
plot(mapping_data, 
     indicator = 'penta3',
     denominator = denominator,
     palette = 'Greens',
     plot_year = mapping_years) +
  cd_report_theme(base_size = 7) +
  theme(
    legend.text = element_text(size = 6),  
    legend.title = element_text(size = 7), 
    panel.border = element_blank(),     
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank(),
    panel.grid = element_blank(),
    aspect.ratio = 1
  )
```

#### Penta1 to Penta3 Dropout

```{r, fig.width=3, fig.height=2.5}
plot(mapping_data, 
     indicator = 'dropout_penta13',
     denominator = denominator,
     palette = 'Reds',
     plot_year = mapping_years) +
  cd_report_theme(base_size = 7) +
  theme(
    legend.text = element_text(size = 6),  
    legend.title = element_text(size = 7), 
    panel.border = element_blank(),     
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank(),
    panel.grid = element_blank(),
    aspect.ratio = 1
  )
```

<!---BLOCK_MULTICOL_STOP{widths: [4,4], space: 0.2, sep: true}--->
