---
title: "Subnational Mapping for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document:
    toc: false
    reference_docx: report-template.docx
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)

library(cd2030)
library(dplyr)
library(purrr)
library(gt)
library(reactable)
library(gridExtra)

cache <- params$cache

adjusted_data <- cache$get_adjusted_data()
country <- cache$get_country()
un_estimates <- cache$get_un_estimates()
rates <- cache$get_national_estimates()
denominator <- cache$get_denominator()
subnational_map <- cache$get_survey_mapping()
mapping_years <- cache$get_mapping_years()

# Function to print notes for a given page
print_notes <- function(page_id, object_id = NULL, parameters = NULL) {
  # Retrieve the notes from the cache
  page_notes <- cache$get_notes(page_id, object_id, parameters) %>% 
    filter(include_in_report == TRUE, !is.null(note))
  
  # Check if there are any notes
  if (nrow(page_notes) > 0) {
    page_notes %>% 
      pull(note) %>% 
      walk(~ cat(paste0(,x, '\n\n')))
  } else {
    cat(paste0("**--- Enter notes related to ", parameters$level, ' ', object_id, ': ', page_id, '. ---**\n\n'))
  }
}
```

## 5. Admin Level 1 Vaccination Coverage Map

### Background

Monitoring the coverage of interventions is a critical and direct output of health 
systems. It is most useful if the national plan has meaningful targets. Both health 
facility and survey data need to be used.

### Measles 1 Mapping -- Admin Level 1

```{r}
mapping_data <- get_mapping_data(adjusted_data, un_estimates, rates, subnational_map)

plot(mapping_data, indicator = 'measles1',
               denominator = denominator,
               palette = 'Greens',
               plot_year = mapping_years,
               title = paste("Distribution of Measles 1 Coverage in ", country, "by Regions")) +
            cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_mapping', 'Measles 1', list(level = 'adminlevel_1'))
```

---

:::

### Penta 3 Mapping -- Admin Level 1

```{r}
plot(mapping_data, indicator = 'penta3',
               denominator = denominator,
               palette = 'Blues',
               plot_year = mapping_years,
               title = paste("Distribution of Penta3 Coverage in ", country, "by Regions")) +
            cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_mapping', 'Penta 3', list(level = 'adminlevel_1'))
```

---

:::

### Penta1 to Penta3 Dropout Mapping -- Admin Level 1

```{r}
plot(mapping_data, indicator = 'dropout_penta13',
               denominator = denominator,
               palette = 'Reds',
               plot_year = mapping_years,
               title = paste("Distribution of Penta1 to Penta3 Dropout in ", country, "by Regions")) +
            cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_mapping', 'Penta1 to Penta3 Dropout', list(level = 'adminlevel_1'))
```

---

:::

### Penta3 to Measles 1 Dropout Mapping -- Admin Level 1

```{r}
plot(mapping_data, indicator = 'dropout_penta3mcv1',
               denominator = denominator,
               palette = 'Purples',
               plot_year = mapping_years,
               title = paste("Distribution of Penta3 to Measles1 Dropout in ", country, "by Regions")) +
            cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_mapping', 'Penta3 to Measles 1 Dropout', list(level = 'adminlevel_1'))
```

---

:::
