---
title: "Subnational Coverage for `r params$country` --- Countdown Analysis"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
  word_document:
    toc: false
    reference_docx: report-template.docx
  pdf_document:
    toc: false
    latex_engine: lualatex
params:
  cache: NULL
  country: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  fig.width=7, 
  fig.height=5, 
  dpi=1200
)

library(cd2030)
library(dplyr)
library(purrr)
library(gt)
library(reactable)
library(gridExtra)

cache <- params$cache

adjusted_data <- cache$get_adjusted_data()
un_estimates <- cache$get_un_estimates()
rates <- cache$get_national_estimates()
denominator <- cache$get_denominator()
wuenic_estimates <- cache$get_wuenic_estimates()
survey_start_year <- cache$get_start_survey_year()
gregion <- cache$get_regional_survey() %>% 
  filter(if(is.null(survey_start_year)) TRUE else year >= survey_start_year)
subnational_map <- cache$get_survey_mapping()
selected_admin_level_1 <- cache$get_admin_level_1()
selected_district <- cache$get_district()

selected_admin_level_1 <- if (is.null(selected_admin_level_1)) {
  sort(unique(adjusted_data$adminlevel_1))[1]
} else {
  selected_admin_level_1
}

selected_district <- if (is.null(selected_district)) {
  sort(unique(adjusted_data$adminlevel_1))[1]
} else {
  selected_district
}

# Function to print notes for a given page
print_notes <- function(page_id, object_id = NULL, parameters = NULL) {
  # Retrieve the notes from the cache
  page_notes <- cache$get_notes(page_id, object_id, parameters) %>% 
    filter(include_in_report == TRUE, !is.null(note))
  
  # Check if there are any notes
  if (nrow(page_notes) > 0) {
    page_notes %>% 
      pull(note) %>% 
      walk(~ cat(paste0(,x, '\n\n')))
  } else {
    cat(paste0("**--- Enter notes related to ", parameters$admin_level, ' ',  object_id, ': ', page_id, '. ---**\n\n'))
  }
}
```

## 5. Admin Level 1 Vaccination Coverage trends {-}

### Background

Monitoring the coverage of interventions is a critical and direct output of health 
systems. It is most useful if the national plan has meaningful targets. Both health 
facility and survey data need to be used.

### Measles 1 Coverage -- Admin Level 1 (`r selected_admin_level_1`)

```{r}
subnational_indicator_coverage <- adjusted_data %>%
          calculate_indicator_coverage(
            admin_level = 'adminlevel_1',
            sbr = rates$sbr,
            nmr = rates$nmr,
            pnmr = rates$pnmr,
            twin = rates$twin_rate,
            preg_loss = rates$preg_loss,
            anc1survey = rates$anc1,
            dpt1survey = rates$penta1)

measles1_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'adminlevel_1',
                         region = selected_admin_level_1,
                         indicator = 'measles1',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)


plot(measles1_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Measles 1', list(admin_level = 'adminlevel_1'))
```

---

:::

### Penta 3 Coverage -- Admin Level 1 (`r selected_admin_level_1`)

```{r}
penta3_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'adminlevel_1',
                         region = selected_admin_level_1,
                         indicator = 'penta3',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(penta3_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta 3', list(admin_level = 'adminlevel_1'))
```

---

:::

### Penta1 to Penta3 Dropout -- Admin Level 1 (`r selected_admin_level_1`)

```{r}
dropout_penta13_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'adminlevel_1',
                         region = selected_admin_level_1,
                         indicator = 'dropout_penta13',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(dropout_penta13_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta1 to Penta3 Dropout', list(admin_level = 'adminlevel_1'))
```

---

:::

### Penta3 to Measles 1 Dropout -- Admin Level 1 (`r selected_admin_level_1`)

```{r}
dropout_penta3mcv1_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'adminlevel_1',
                         region = selected_admin_level_1,
                         indicator = 'dropout_penta3mcv1',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(dropout_penta3mcv1_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta3 to Measles 1 Dropout', list(admin_level = 'adminlevel_1'))
```

---

:::


## 5. District Vaccination Coverage trends {-}

### Background

Monitoring the coverage of interventions is a critical and direct output of health 
systems. It is most useful if the national plan has meaningful targets. Both health 
facility and survey data need to be used.

### Measles 1 Coverage -- District (`r selected_district`)

```{r}
subnational_indicator_coverage <- adjusted_data %>%
          calculate_indicator_coverage(
            admin_level = 'district',
            sbr = rates$sbr,
            nmr = rates$nmr,
            pnmr = rates$pnmr,
            twin = rates$twin_rate,
            preg_loss = rates$preg_loss,
            anc1survey = rates$anc1,
            dpt1survey = rates$penta1)

measles1_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'district',
                         region = selected_district,
                         indicator = 'measles1',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)


plot(measles1_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Measles 1', list(admin_level = 'district'))
```

---

:::

### Penta 3 Coverage -- District (`r selected_district`)

```{r}
penta3_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'district',
                         region = selected_district,
                         indicator = 'penta3',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(penta3_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta 3', list(admin_level = 'district'))
```

---

:::

### Penta1 to Penta3 Dropout -- District (`r selected_district`)

```{r}
dropout_penta13_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'district',
                         region = selected_district,
                         indicator = 'dropout_penta13',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(dropout_penta13_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta1 to Penta3 Dropout', list(admin_level = 'district'))
```

---

:::

### Penta3 to Measles 1 Dropout -- District (`r selected_district`)

```{r}
dropout_penta3mcv1_coverage <- analyze_coverage(subnational_indicator_coverage,
                         admin_level = 'district',
                         region = selected_district,
                         indicator = 'dropout_penta3mcv1',
                         subnational_map = subnational_map,
                         denominator = denominator,
                         survey_data = gregion,
                         wuenic_data = wuenic_estimates)

plot(dropout_penta3mcv1_coverage) + cd_report_theme()
```

#### ðŸ“ Notes 

::: {custom-style="Style1"}

---

```{r, results='asis'}
print_notes('subnational_coverage', 'Penta3 to Measles 1 Dropout', list(admin_level = 'district'))
```

---

:::
